%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES & FORMATTING
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
% page padding
\usepackage[scale=0.93]{geometry}
% \usepackage[top=1cm, bottom=1cm, left=1.5cm, right=1.5cm]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{supertabular}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{titlesec}				
\usepackage{fontawesome5}
\usepackage[unicode, draft=false]{hyperref}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

% custom section with rule
\titleformat{\section}{\color{linkcolour}\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

% hyperlink colours
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

%page paddinng 

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	HEADER (Name + Icons)
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Govind Gupta} \\[7.5pt]
\href{https://github.com/govindggupta}{\raisebox{-0.05\height}\faGithub\ govindggupta} \ $|$ \ 
\href{https://linkedin.com/in/govindggupta}{\raisebox{-0.05\height}\faLinkedin\ govindggupta} \ $|$ \ 
\href{https://govindgupta.me}{\raisebox{-0.05\height}\faGlobe \ govindgupta.me} \ $|$ \ 
\href{mailto:govind12771277@gmail.com }{\raisebox{-0.05\height}\faEnvelope \ govind12771277@gmail.com} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}
Third-year undergraduate with a strong interest in full-stack development, AI agents, RAG systems, and LLM-based applications. Enjoy building software that solves real-world problems, with a focus on turning ideas into scalable and impactful products. Quick to adapt to new technologies and driven by continuous learning.

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}X r@{}}	
\textbf{Bachelor of Technology in Computer Science} & Aug 2023 -- Present \\
Uka Tarsadia University, Surat, Gujarat & \\
CGPA: 7.47 / 10, SGPA: 7.57 / 10 (6th Sem) & \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}



% Pulse Board Project
\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Pulse Board} & \hfill \href{https://pulseboard.govindgupta.me}{Live} $|$ \href{https://github.com/govindggupta/pulseboard}{GitHub} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{\begin{itemize}[nosep, leftmargin=1em, label=--, topsep=5pt, before=\vspace{-\baselineskip}, after=\vspace{-4pt}]
   \item Real-time polling platform that allows users to create, share, and participate in live polls with instant result visualization and secure voting.
   \item Supports anonymous or authenticated voting with live chart updates via Socket.io; used for team retrospectives and classroom polls.
   \item React.js, TypeScript, Node.js, Express.js, Socket.io, PostgreSQL, Redis, Docker.
\end{itemize}} \\
\end{tabularx}
\vspace{8pt}

% Draw App Project
\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Draw App} & \hfill \href{https://github.com/govindggupta/draw-app}{GitHub} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[nosep, leftmargin=1em, label=--, topsep=5pt, before=\vspace{-\baselineskip}, after=\vspace{-4pt}]
    \item Real-time collaborative drawing application where multiple users can join a room and draw simultaneously on a shared canvas with synchronized strokes and color picker.
    \item Built as a monorepo using Turborepo for managing shared packages and separate frontend/backend deployments.
   \item React.js, TypeScript, WebSocket, Node.js, Express.js, PostgreSQL, Turborepo, Docker.
\end{itemize}
} \\
\end{tabularx}
\vspace{8pt}

% Draw App Project
\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Brainly} & \hfill \href{https://github.com/govindggupta/brainly}{GitHub} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[nosep, leftmargin=1em, label=--, topsep=5pt, before=\vspace{-\baselineskip}, after=\vspace{-4pt}]
     \item Full-stack "Second Brain" app for saving, organizing, and retrieving useful links, notes, and content with personal dashboard and tag-based categorization.
    \item Share your entire collection via a unique public slug URL — anyone with the link can view your curated content without logging in.
    \item MongoDB, Express.js, React, Node.js, Docker, JWT authentication, Tailwind CSS.
\end{itemize}
} \\
\end{tabularx}
\vspace{8pt}



%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages: &  Python, C, C++, JavaScript, TypeScript, SQL, HTML/CSS \\
Technologies: & React, Node.js, Express, MongoDB, Tailwind CSS, Socket.io \\
Tools: & VS Code, GitHub, Postman, Cloudinary \\
Relevant Coursework: & Web Development, Data Structures, Algorithms, System Design, Database Management \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	ACHIEVEMENTS & AWARDS
%----------------------------------------------------------------------------------------
\section{Achievements \& Awards}
\begin{itemize}[nosep, leftmargin=1em, label=--]
  \item Secured funding under SSIP (Student Start-Up Induction Program) for the project "Air Purifier."
  \item Robo War Winner at college Tech Fest.
\end{itemize}

%----------------------------------------------------------------------------------------
%	FOOTER (LAST UPDATED)
%----------------------------------------------------------------------------------------
\center{\footnotesize Last updated: \today}
\end{document}
